Component-Based mruby Platform for IoT Devices

### 2017-11-15 ipsj/paper.tex
Fix title
Add Dynamic Connection

\title{Component-based Software Development Framework \\for Embedded IoT Devices（仮）}

@@

@@

>>>>

\title{Component-Based mruby Platform for IoT Devices}

@@

\subsubsection{Dynamic connection in TECS}
\label{sec:DynamicConnection}

\begin{figure}[t]
    \centering
    \includegraphics[width=7.0cm,clip]{figure/DynamicConnection.pdf}
    \vspace{-3mm} \caption{Dynamic connection}
    \vspace{-1mm} \label{fig:DynamicConnection}
\end{figure}

TECS supports a dynamic connection, a method for switching the binding of components at runtime (Fig. \ref{fig:DynamicConnection}) as a new functionality.
In Fig. \ref{fig:DynamicConnection}, the solid line represents binding and the dotted line represents non-binding.
Note that all components are statically generated in TECS, which can optimize the overhead of componentization because components are statically configured.
Dynamically generating components causes a good deal of memory consumption, which is a serious problem for embedded systems with strict memory constraints.
The proposed framework can take advantage of the componentization in TINET while satisfying the memory constraint because components are statically generated and dynamically connected in TECS.

TINET+TECS utilizes the dynamic connection to switch between CEP and REP components, as shown in Fig. \ref{fig:DynamicConnectionUseCase}.
In a server application, CEP is associated with REP in the state of waiting for a connection request from clients\footnote{tcp\_acp\_cep(ID cepid, ID repid, T\_IPV4EP *p\_dstaddr, TMO tmout).}.
For example, when processing with the HTTP protocol, CEP passively opens with an REP of port number 80.

\begin{figure}[t]
    \centering
    \includegraphics[width=7.0cm,clip]{figure/DynamicConnectionUseCase.pdf}
    \caption{Dynamic connection between CEP and REP}
    \label{fig:DynamicConnectionUseCase}
\end{figure}

To utilize dynamic connectivity, a selector should be defined.
A selector connects all components that can be dynamically connected under a common descriptor that serves as an identifier to access each component \cite{par:optimization}.
The cREP ports form a call port array connecting to connecting to all tREP cells (Line 8 in Fig. \ref{src:DynamicCDLcode}).
{\it [ref\_desc]} is used to identify call ports referring to descriptors. 
In the case shown in Fig. \ref{fig:DynamicConnectionUseCase}, the tRepSelector cell connects all tREP cells.

A CEP component has two call ports: the cRepSelector port, which connects to the eRepSelector port of tRepSelector cell, and the cREP4 port, which connects to either of the tREP cells (Lines 11--13 in Fig. \ref{src:DynamicCDLcode}).
The cREP port is defined using {\it [dynamic]} to identify the call port used to dynamically switch the components.
The call port with the {\it [dynamic]} specifier is not optimized and is allocated in RAM using a plug-in.

\begin{figure}[t]
\centering
\begin{lstlisting}
signature sRepSelector {
    void  getRep([out]Descriptor(sREP4) *desc,
                 [in]int_t i);
};
celltype tRepSelector {
    entry sRepSelector eRepSelector;
    [ref_desc]
        call sREP4 cREP[NUM_REP];
};
celltype tTCPCEP {
    call sRepSelector cRepSelector;
    [dynamic]
        call sREP4 cREP;
    /* Omit: other call/entry ports */
    /* Omit: attributes and variables */
};
\end{lstlisting}
\caption{Signature and celltype description for the dynamic connection}
\label{src:DynamicCDLcode}
\end{figure}

Fig. \ref{src:DynamicCcode} shows a sample code of the dynamic connection.
The eAPI\_accept function is the function wrapping {\it tcp\_acp\_cep} under TECS, which is set as the state waiting for a connection request.
The dynamic connection in the function is performed as shown in Fig. \ref{src:DynamicCcode}.
First, the descriptor of REP to be joined is obtained (Line 3 in Fig. \ref{src:DynamicCcode}).
The first argument, {\it \&desc}, is a variable used to store the descriptor information, whereas the second argument, {\it repid}, is the index of tREP cells.
Next, the descriptor is set (Line 5 in Fig. \ref{src:DynamicCcode}), and the cREP port combines the tREP cell specified by the descriptor, enabling the tCEP cell to call the function of the tREP cell to be joined (Line 7 in Fig. \ref{src:DynamicCcode}).

\begin{figure}[t]
\centering
\begin{lstlisting}
eAPI_accept (.., ..) {
    /* Get a descriptor of intended REP cell */
    cRepSelector_getRep(&desc, repid);
    /* Set the descriptor */
    cREP_set_descriptor(desc);
    /* Call the function of intended REP cell */
    cREP_getEndpoint();
}
\end{lstlisting}
\caption{Accept function (a dynamic connection example)}
\label{src:DynamicCcode}
\end{figure}

@@

\subsection{Dynamic connection}

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/ComparisonOfDynamicConnection.pdf}
    \vspace{-1mm} \caption{Component diagrams for without/with the dynamic connection cases}
    \vspace{-1mm} \label{fig:ComparisonOfDynamicConnection}
\end{figure}

Memory consumption without and with TECS dynamic connection was then evaluated.
As shown in the left panel of Fig. \ref{fig:ComparisonOfDynamicConnection}, each CEP component should be statically connected to all REP components if the dynamic connection is not used.
As the number of REPs increases, additional call ports of CEP are required, in turn increasing the consumption of memory. 
The dynamic connection reduces memory consumption because only one CEP-to-REP call port is required per CEP, as illustrated with red lines in the right panel of Fig. \ref{fig:ComparisonOfDynamicConnection}.
Even if the number of REPs increases, additional call ports can be joined through the selector, instead of the CEPs.

Memory consumption of without and with dynamic connection is shown in TABLE \ref{fig:EvaluationOfDynamicConnection}.
The dynamic connection case consumes the more RAM memory because, as mentioned in Section \ref{sec:DynamicConnection}, call ports with {\it [dynamic]} are not optimized and allocated in RAM areas.
However, the overall memory consumption is lower under the proposed framework.

% \begin{figure}[t]
%     \centering
%     \includegraphics[width=8.0cm,clip]{figure/EvaluationOfDynamicConnection.pdf}
%     \vspace{-1mm} \caption{Memory consumption in two cases (with/without dynamic connection)}
%     \vspace{-1mm} \label{fig:EvaluationOfDynamicConnection}
% \end{figure}
\begin{table}[t]
    \centering
    \caption{Memory consumption in two cases\protect\linebreak (with/without dynamic connection)}
    {\tabcolsep = 1mm
    \begin{tabular}{c|r|r|r|r}
        \hline\hline
                &  CEP:1 REP:1 & CEP:1 REP:5 & CEP:2 REP:5 & CEP:5 REP:10 \\ \hline
        without &  324.98 KB   & 325.34 KB   & 326.39 KB   & 331.68 KB   \\
        with    &  325.23 KB   & 325.32 KB   & 327.24 KB   & 330.48 KB   \\
        \hline
    \end{tabular}
    }
    \label{fig:EvaluationOfDynamicConnection}
\end{table}

\begin{table}[t]
    \centering
    \caption{CDL code lines of without/with dynamic connection}
    \begin{tabular}{l|r|r|r}
        \hline\hline
                     &  without  &  with  &  Diff  \\ \hline
        CEP:1 REP:1  &  344 lines     &  347 lines  &  -3 lines   \\
        CEP:1 REP:5  &  369 lines     &  367 lines  &   2 lines   \\
        CEP:2 REP:5  &  387 lines     &  382 lines  &   5 lines   \\
        CEP:5 REP:10 &  485 lines     &  445 lines  &  40 lines   \\
        \hline
    \end{tabular}
    \label{tab:EvaluationOfConfigurabilityByDynamicConnection}
\end{table}

\begin{figure}[t]
 \centering
 \begin{lstlisting}
/* without Dynamic Connection */
cell tTCPCEP TCPCEP_000 {
    cREP[0] = REP_000.eREP;
    ..
    cREP[n] = REP_00n.eREP;
};
cell tTCPCEP TCPCEP_001 {
    cREP[0] = REP_000.eREP;
    ..
    cREP[n] = REP_00n.eREP;
};
..
cell tTCPCEP TCPCEP_00n {
    cREP[0] = REP_000.eREP;
    ..
    cREP[n] = REP_00n.eREP;
};
 \end{lstlisting}
 \centering
 \begin{lstlisting}
/* with Dynamic Connection */
cell tRepSelector RepSelector {
    cREP[0] = REP_000.eREP;
    ..
    cREP[n] = REP_00n.eREP;
};
cell tTCPCEP TCPCEP_000 {
    cRepSelector = RepSelector.eRepSelector;
};
cell tTCPCEP TCPCEP_001 {
    cRepSelector = RepSelector.eRepSelector;
};
..
cell tTCPCEP TCPCEP_00n {
    cRepSelector = RepSelector.eRepSelector;
};
 \end{lstlisting}
 \caption{Two CDL codes (without/with dynamic connection)}
 \label{src:ComparisonOfCDL}
\end{figure}

The code lines in CDL of without and with the dynamic connection is shown in TABLE \ref{tab:EvaluationOfConfigurabilityByDynamicConnection} to demonstrate improved configurability.
As the number of CEPs and REPs increases, the amount of CDL code lines to be added increases.
In the left panel of Fig. \ref{fig:ComparisonOfDynamicConnection}, each CEP connects all REPs as shown in the upper of Fig. \ref{src:ComparisonOfCDL}. 
In the right panel of Fig. \ref{fig:ComparisonOfDynamicConnection}, a CEP dynamically connects an REP, and only the selector connects all REPs as shown in the lower of Fig. \ref{src:ComparisonOfCDL}. 
It is effective for software that uses many ports because the difference spreads as the number of CEPs and REPs increases.
